A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-10-29 paper/main.tex
some cleaning
Minor language tuning

\begin{abstract}
% up to 300 words intro
Here we present an annotation of speech spoken in the audio-visual movie
``Forrest Gump'' and its audio-description (i.e. the audio-only variant of the
movie) as an addition to a large public functional brain imaging dataset
(\href{www.studyforrest.org}{studyforrest.org}).
% anno content 1
The annotation provides information about the exact timing of each of the more
than 2500 spoken sentences, 16000 words (including 202 non-speech
vocalizations), 66000 phonemes, and their corresponding speaker.
% anno content 2
Additionally for every word, we provide lemmatization, a simple
part-of-speech-tagging (15 grammatical categories), a detailed part-of-speech
tagging (43 grammatical categories), syntactic dependencies, and a semantic
analysis based on word embedding which represents each word in a
300-dimensional semantic space.
% validation
To validate the dataset's quality, we build a model of hemodynamic brain
activity based on information drawn from the annotation.
% why bother
Results suggest that the annotation's content and quality enable independent
researchers to create models of brain activity correlating with a
variety of linguistic aspects under conditions of real-life complexity.
\end{abstract}

@@

\listoftodos

@@

\section*{Introduction}
% intro to intro
Cognitive and psychiatric neuroimaging are moving towards studying brain
functions under conditions of lifelike complexity
\citep{sonkusare2019naturalistic, eickhoff2020towards}. Motion pictures
\citep{hasson2008neurocinematics} and continuous narratives
\citep{wilson2008beyond, lerner2011topographic} are increasingly utilized as so called ``naturalistic
stimuli''.
% not designed for research
Naturalistic stimuli are usually designed for commercial purposes and to
entertain their audiences.
% thus annotation bottleneck
Thus, the temporal structure of their feature space is usually not explicitly
known leading to an ``annotation bottleneck'' \citep{aliko2020naturalistic} when
used for neuroscientific research.

% data-driven methods..
Data-driven methods like inter-subject correlation
(ISC)\citep{hasson2004intersubject} or independent component analysis
(ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
corresponding fMRI data circumventing this bottleneck.
% ..are nice but:
However, data-driven methods alone fall usually short of pinpointing their
results to specific stimulus events \citep{kauttonen2015optimizing}.
% model-driven methods
Model-driven methods, like a general linear model (GLM), that are based on
stimulus annotations can be useful to test hypotheses on specific brain
functions under more ecologically valid conditions, to statistically control
confounding stimulus features, and to explain not just ``how'' the brain is
responding to a stimulus but also ``why'' \citep{hamilton2018revolution}.
% GLM: example studies
Studies using GLMs based on annotations of a stimulus' temporal structure have
elucidated for example how the brain responds to visual features of a movie
\citep{bartels2004mapping} or speech-related features of a narrative
\citep{rocca2020language}.
% combination of data-driven and model-driven approaches
Furthermore, stimulus annotations can inform data-driven methods about a
stimulus' temporal dynamics, or model-driven and data-driven methods can be
combined to improve the interpretability of results \citep{lahnakoski2012stimulus}.

@@

osf.io: The annotation as both a TSV and TextGrid file as well as scripts and
data of the analysis, doi:
\href{dx.doi.org/10.17605/OSF.IO/GFRME}{10.17605/OSF.IO/GFRME}

>>>>

\begin{abstract}
% up to 300 words intro
Here we present an annotation of speech in the audio-visual movie
``Forrest Gump'' and its audio-description for a visually impaired audience,
as an addition to a large public functional brain imaging dataset
(\href{www.studyforrest.org}{studyforrest.org}).
% anno content 1
The annotation provides information about the exact timing of each of the more
than 2500 spoken sentences, 16000 words (including 202 non-speech
vocalizations), 66000 phonemes, and their corresponding speaker.
% anno content 2
Additionally, for every word, we provide lemmatization, a simple
part-of-speech-tagging (15 grammatical categories), a detailed part-of-speech
tagging (43 grammatical categories), syntactic dependencies, and a semantic
analysis based on word embedding which represents each word in a
300-dimensional semantic space.
% validation
To validate the dataset's quality, we build a model of hemodynamic brain
activity based on information drawn from the annotation.
% why bother
Results suggest that the annotation's content and quality enable independent
researchers to create models of brain activity correlating with a
variety of linguistic aspects under conditions of near-real-life complexity.
\end{abstract}

@@

@@

\section*{Introduction}
% intro to intro
Cognitive and psychiatric neuroimaging are moving towards studying brain
functions under conditions of lifelike complexity
\citep{sonkusare2019naturalistic, eickhoff2020towards}. Motion pictures
\citep{hasson2008neurocinematics} and continuous narratives
\citep{wilson2008beyond, lerner2011topographic} are increasingly utilized as so called ``naturalistic
stimuli''.
% not designed for research
Naturalistic stimuli are usually designed for commercial purposes and to
entertain their audiences.
% thus annotation bottleneck
Thus, the temporal structure of their feature space is usually not explicitly
known, leading to an ``annotation bottleneck'' \citep{aliko2020naturalistic} when
used for neuroscientific research.

% data-driven methods..
Data-driven methods like inter-subject correlation
(ISC)\citep{hasson2004intersubject} or independent component analysis
(ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
such fMRI data in order to circumvent this bottleneck.
% ..are nice but:
However, use of data-driven methods alone falls short of associating results with
particular stimulus events \citep{kauttonen2015optimizing}.
% model-driven methods
Model-driven methods, like the general linear model (GLM), that are based on
stimulus annotations can be useful to test hypotheses on specific brain
functions under more ecologically valid conditions, to statistically control
confounding stimulus features, and to explain not just ``how'' the brain is
responding to a stimulus but also ``why'' \citep{hamilton2018revolution}.
% GLM: example studies
Studies using GLMs based on annotations of a stimulus' temporal structure have
elucidated, for example, how the brain responds to visual features of a movie
\citep{bartels2004mapping} or speech-related features of a narrative
\citep{rocca2020language}.
% combination of data-driven and model-driven approaches
Furthermore, stimulus annotations can inform data-driven methods about a
stimulus' temporal dynamics, or model-driven and data-driven methods can be
combined to improve the interpretability of results \citep{lahnakoski2012stimulus}.

@@

osf.io: The annotation as both a tab-separated values (TSV) formatted table and
TextGrid file as well as scripts and data of the analysis, doi:
\href{dx.doi.org/10.17605/OSF.IO/GFRME}{10.17605/OSF.IO/GFRME}
